Pandemic Pass

### 2023-02-14 analysis/presentations/2022-11-04_peace-science.qmd
Remove old references to old plugins

---
title: "Pandemic Pass"
subtitle: "Treaty Derogations and<br>Human Rights Practices During COVID-19"
author:
  - name: Suparna Chaudhry
    affiliation: Lewis and Clark College
  - name: Audrey Comstock
    affiliation: Arizona State University
  - name: Andrew Heiss
    affiliation: Georgia State University
date: "November 4, 2022"
date-format: long
output: revealjs
format:
  revealjs: 
    slide-number: true
    chalkboard:
      buttons: true
    preview-links: auto
    footer: "Chaudhry, Comstock, and Heiss&emsp;|&emsp;Pandemic Pass"
    # include-before-body: testing.html
    # revealjs-plugins:
    #   - simplemenu
    theme: [simple, custom.scss]
    title-slide-attributes:
      data-background-color: "#c06636"
# resources:
  # - slides.pdf
---

>>>>

---
title: "Pandemic Pass"
subtitle: "Treaty Derogations and<br>Human Rights Practices During COVID-19"
author:
  - name: Suparna Chaudhry
    affiliation: Lewis and Clark College
  - name: Audrey Comstock
    affiliation: Arizona State University
  - name: Andrew Heiss
    affiliation: Georgia State University
date: "November 4, 2022"
date-format: long
output: revealjs
format:
  revealjs: 
    slide-number: true
    chalkboard:
      buttons: true
    preview-links: auto
    footer: "Chaudhry, Comstock, and Heiss&emsp;|&emsp;Pandemic Pass"
    theme: [simple, custom.scss]
    title-slide-attributes:
      data-background-color: "#c06636"
# resources:
  # - slides.pdf
---
